---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# ACmisc
```{r setup,echo=F}
library(ACmisc)
```

[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)


## Overview to ACmisc

Various functions used by Aaron Cochrane, and encouraged for collaborators to use. Please don't hesitate to branch, submit pull requests, etc., or to contact Aaron directly.

## Installing the package

The R package `devtools` includes a very easy way to install packages from Github.

```
devtools::install_github('akcochrane/ACmisc', build_vignettes = TRUE)
```

## A couple example functions

### `BICBF()` -- Bayes Factors for common models

Calculates BIC for the entire lm(), rlm(), glm(), lmer(), or glmer() model, and for the entire set of models dropping each fixed effect one at a time. Uses the change in BIC between models to approximate Bayes Factors (essentially penalized Likelihood Ratios, or evidence for one model over another). Follows the recommendations of Wagenmakers (2007; PBR)

```{r BICBF_glmer, warning=F, message=F}
library(lme4)
mod <- lmer(mot ~ nback * ravens + (1|isAdult),dat_cochraneEtAl_2019_PLOSOne)

BF_table <- BICBF(mod)
knitr::kable(BF_table,digits=3)
```

### `d1iso()`

Extracts scores from a single isotonic [think: rank-based] underlying dimension from multivariate data. Very useful for extracting the common variation in data when other methods (e.g., PCA) would struggle due to different variables' lack of Gaussian-ness.

### `ddm_dr_lm()` -- Drift Diffusion Linear Model

Essentially fits a generalized linear model for a Wiener process, using the density estimation function from the RWiener package. First fits a standard 4-parameter Wiener model to the entire RT+response-category vector. Then uses the boundary separation, bias, and non-decision time from this overall model, and finds the best set of parameters to create a drift rate vector as a linear function of the right-hand side of formIn. __Only numeric predictors have been tested.__ 

### `findLowerRT()`

Follows the procedure of Ratcliff & Tuerlinckx (2002) to find the lowest RT at which accuracy is below chance.